*cellcount*: an open-source and automated approach to cyanobacteria enumeration

### 2023-03-03 manuscript_files/draft_manuscript.Rmd
Updates to authorship

  - name: David E. Berthold
    affiliation: Department of Biological Sciences, Florida International University, Miami, FL 33199, USA

  - name: H. Dail Laughinghouse
    affiliation: Department of Biological Sciences, Florida International University, Miami, FL 33199, USA
    orcid_id: 0000-0003-1018-6948

  - name: Brandon Boyd
    affiliation: U.S. Army Corps of Engineers, Engineer Research and Development Center, Vicksburg, MS 39180, USA

>>>>

#  - name: David E. Berthold
#    affiliation: Department of Biological Sciences, Florida International University, Miami, FL 33199, USA

#  - name: H. Dail Laughinghouse
#    affiliation: Department of Biological Sciences, Florida International University, Miami, FL 33199, USA
#    orcid_id: 0000-0003-1018-6948
